%==== PACKAGES AND OTHER DOCUMENT CONFIGURATIONS  ====%
% Base document class and page margins
\documentclass{resume}
\usepackage[left=0.25in,top=0.25in,right=0.25in,bottom=0.25in]{geometry}

% Font and symbol packages
\usepackage[T1]{fontenc}      % Better font encoding for special characters
\usepackage{lmodern}          % Modern font family
\usepackage{fontawesome}      % Icons for contact information
\usepackage{textcomp}         % Additional text symbols

% Hyperlink and color configuration
\usepackage{xcolor}           % Custom color support
\usepackage{hyperref}         % Hyperlink support
\definecolor{myblue}{RGB}{0, 164, 218}  % Custom blue color for links

\hypersetup{
    colorlinks=true,          % Enable colored links
    linkcolor=myblue,         % Internal link color
    citecolor=myblue,         % Citation link color
    urlcolor=myblue          % URL link color
}

%==== Headings ====%
\name{Artur Grygorian} % Your name
\address{
{\faEnvelope} \href{mailto:arturgrygorian3@gmail.com}{arturgrygorian3@gmail.com} \quad {\faGithub} \href{https://github.com/ArturG93}{https://github.com/ArturG93} \quad {\faLinkedin} \href{https://www.linkedin.com/in/arturgrygorian/}{https://www.linkedin.com/in/arturgrygorian/}}
\address{Remote, Germany}

\begin{document}

%==== SUMMARY SECTION ====%
% Conditional section that displays professional summary if provided
\begin{rSection}{Summary}
    Experienced Machine Learning Engineer with over 6 years of hands-on experience in building and deploying AI solutions at scale. Proven track record in leading cross-functional teams, designing and implementing machine learning infrastructure, and optimizing model performance. Skilled in generative AI, LLMs, and cloud-based AI integrations, with a focus on responsible AI practices and open-source contributions. Seeking to leverage my expertise in AI and collaborative leadership to drive innovation in Firefox's Generative AI initiatives at Mozilla.
\end{rSection}

%==== WORK EXPERIENCE SECTION =====%
% Iterates through work experiences, formatting each with:
% - Role and date range
% - Company and location
% - Bullet points for responsibilities/achievements
    \begin{rSection}{Work Experience}
                    {\textbf{Sr. Manager Analytics (Global Fulfilment Speed)}} \hfill {Aug 2022 - Aug 2024}
            \\ % Line break
            {\normalfont{\textit{Wayfair}}} \hfill {\normalfont{\textit{Berlin, Germany}}}
            \begin{list}{\tiny$\bullet$}{ % Matching education's bullet style
                \leftmargin=1em
                \itemsep=-0.5em
                \vspace{-0.5em}
            }
                            \item Led global analytics team across EU, UK, and USA, implementing machine learning solutions to improve delivery promise accuracy, resulting in 1500 bps boost in speed badging and USD 5M annual revenue increase.
                            \item Designed and implemented A/B testing framework with ML engineers to measure conversion impact of faster delivery promises, guiding strategic initiatives and ROI estimation.
                            \item Built and mentored a high-performing team of 5+ data scientists and analytics engineers, focusing on delivering quality AI solutions and analytics insights.
                        \end{list}
            \vspace{0.1em}
                    {\textbf{Analytics Manager (EU Fulfilment Speed)}} \hfill {Jun 2021 - Aug 2022}
            \\ % Line break
            {\normalfont{\textit{Wayfair}}} \hfill {\normalfont{\textit{Berlin, Germany}}}
            \begin{list}{\tiny$\bullet$}{ % Matching education's bullet style
                \leftmargin=1em
                \itemsep=-0.5em
                \vspace{-0.5em}
            }
                            \item Developed a machine learning model to estimate delivery time for the EU network, improving speed by 1.3 days and generating an additional EUR 10M in annual revenue.
                            \item Established KPIs and designed dashboards to evaluate delivery network health, leading weekly and monthly business reviews with executive leadership.
                            \item Orchestrated cross-functional collaboration for high-volume events, ensuring alignment and buy-in for AI-driven initiatives across the company.
                        \end{list}
            \vspace{0.1em}
                    {\textbf{Analytics Manager (Delivery Speed)}} \hfill {Sep 2019 - Apr 2021}
            \\ % Line break
            {\normalfont{\textit{The Home Depot}}} \hfill {\normalfont{\textit{Atlanta, GA, USA}}}
            \begin{list}{\tiny$\bullet$}{ % Matching education's bullet style
                \leftmargin=1em
                \itemsep=-0.5em
                \vspace{-0.5em}
            }
                            \item Created a machine learning model that improved delivery promise by 0.7 days without impacting reliability, resulting in more than USD 100M annual revenue increase through higher conversion.
                            \item Developed data pipelines using SQL Server and Google BigQuery to integrate carrier, warehouse, and customer data for comprehensive network analysis.
                            \item Established and led a data science team of 3 from inception, guiding them to become one of the most impactful teams in the organization, earning multiple company awards.
                        \end{list}
            \vspace{0.1em}
            \end{rSection}

%==== EDUCATION SECTION ====%
% Displays academic credentials with:
% - Degree and date range
% - University name
% - Optional achievements/honors
\begin{rSection}{Education}
            {\textbf{Master's in Statistics}} \hfill {2015 - 2017}
        \\ % Line break
        {\normalfont{\textit{Georgia Southern University}}}
                    \begin{list}{\tiny$\bullet$}{ % Changed to smaller bullet
                \leftmargin=1em
                \itemsep=-0.5em
                \vspace{-0.5em}
            }
                            \item Best Graduate Assistant Award
                            \item GPA 4.0/4.0
                        \end{list}
                \vspace{0.1em}
            {\textbf{Master's in Economics}} \hfill {2012 - 2014}
        \\ % Line break
        {\normalfont{\textit{Kyiv School of Economics}}}
                    \begin{list}{\tiny$\bullet$}{ % Changed to smaller bullet
                \leftmargin=1em
                \itemsep=-0.5em
                \vspace{-0.5em}
            }
                            \item Won KPMG Case Competition Ukraine
                            \item Finalist of EY Case Competition Ukraine
                        \end{list}
                \vspace{0.1em}
            {\textbf{Master's in Mathematics}} \hfill {2007 - 2013}
        \\ % Line break
        {\normalfont{\textit{Odesa National University}}}
                \vspace{0.1em}
    \end{rSection}

%==== CERTIFICATIONS SECTION ====%
% Lists professional certifications including:
% - Certificate name with link
% - Issuing organization
% - Description and technologies
% - Related project details if available
\begin{rSection}{Certifications \& Training}
            {\href{https://coursera.org/share/9459a80d6710c6beebe8355a73b52368}{\textbf{Generative AI with Large Language Models}}} \hfill {October 2023}
        \\ % Line break
        {\normalfont{\textit{Coursera, DeepLearning.AI}}}
        \\ % Added line break for description
        Comprehensive course on Generative AI and LLMs, covering model optimization, advanced techniques, and practical applications. % Description on new line
        \\
        \textbf{Technologies:} Generative AI fundamentals, transformer architecture, LLMs, model optimization, RLHF, chain-of-thought prompting
        \\
                
          % Add space only if it's not the last certification
            \vspace{0.1em}
                    {\href{https://certificate.datatalks.club/llm-zoomcamp/2024/55db812d19a5b355790d127cb88ca72afdc49df5.pdf}{\textbf{LLM Bootcamp}}} \hfill {Oct 2024}
        \\ % Line break
        {\normalfont{\textit{DataTalks.Club}}}
        \\ % Added line break for description
        Intensive bootcamp covering LLMs, RAG, and advanced AI techniques for production deployment. % Description on new line
        \\
        \textbf{Technologies:} LLMs, RAG, OpenAI API, HuggingFace Hub, Ollama, vector databases, LangChain
        \\
                    \textbf{Project:} \href{https://github.com/ArturGR3/food_search_RAG}{RAG for Recipe Recommendation System} - 
            Developed a RAG-based recipe recommendation system to demonstrate practical application of LLMs in information retrieval and personalization.
                
          % Add space only if it's not the last certification
            \vspace{0.1em}
                    {\href{https://certificate.datatalks.club/mlops-zoomcamp/2024/55db812d19a5b355790d127cb88ca72afdc49df5.pdf}{\textbf{MLOps Bootcamp}}} \hfill {Sep 2024}
        \\ % Line break
        {\normalfont{\textit{DataTalks.Club}}}
        \\ % Added line break for description
        Comprehensive MLOps training covering experiment tracking, model deployment, and monitoring. % Description on new line
        \\
        \textbf{Technologies:} MLflow, workflow orchestration, model deployment, Prometheus, Grafana
        \\
                    \textbf{Project:} \href{https://github.com/ArturGR3/MLOps-project}{End to End ML Deployment Using AutoGluon and OpenFE} - 
            Implemented an end-to-end ML deployment pipeline to showcase MLOps best practices and automate the ML lifecycle.
                
            \end{rSection}

%==== PROJECTS SECTION ====%
% Showcases significant projects with:
% - Project name with link
% - Organization (if applicable)
% - Project purpose
% - Technologies used
\begin{rSection}{Projects}
            {\href{https://github.com/ArturGR3/Youtube-transcript-Q-A}{\textbf{YouTube Transcript Analyzer}}} \hfill {Oct 2024}
        \\
        Developed an AI-powered tool for analyzing YouTube video transcripts, demonstrating practical application of LLMs and API integration.
        \\
        \textbf{Technologies:} YouTube Transcript API, LLM integration, Instructor library, CSV handling, token estimation, API cost calculation
        
          % Add space only if it's not the last project
            \vspace{0.1em}
                    {\href{https://github.com/ArturGR3/LLM-kaggle-competition}{\textbf{LLM Kaggle Winning Solution}}} \hfill {Sep 2024}
        \\
        Created a winning solution for a Kaggle competition using advanced LLM techniques, showcasing expertise in AI problem-solving and optimization.
        \\
        \textbf{Technologies:} Claude-3.5 Sonnet LLM, zero-shot chain of thought reasoning, LLM Python code generation, Instructor library, multithreading
        
            \end{rSection}

%==== TECHNICAL SKILLS SECTION ====%
% Organized list of technical competencies
% Grouped by category (e.g., Languages, Frameworks, etc.)
\begin{rSection}{Technical Skills}
    \begin{description}
                    \item[\textbf{Machine Learning and AI:}] \raggedright PyTorch, TensorFlow, Scikit-learn, AutoGluon, MLflow, RAG, LangChain, OpenAI API, Anthropic, Ollama\\[0.3ex]
                    \item[\textbf{Cloud and Infrastructure:}] \raggedright AWS, GCP, Docker, Distributed systems\\[0.3ex]
                    \item[\textbf{Programming and Data Analysis:}] \raggedright Python, SQL, R\\[0.3ex]
                    \item[\textbf{MLOps and Development Tools:}] \raggedright GitHub, MLflow, Makefile, Prometheus, Grafana\\[0.3ex]
                    \item[\textbf{Soft Skills:}] \raggedright Cross-functional collaboration, Technical leadership, Problem-solving, Communication\\[0.3ex]
            \end{description}
\end{rSection}

\end{document}